An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-09 poly-embed-journal/poly-embed-journal.tex
Unifying the margin comments

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewer}[1]{\reviewerresponse{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewer{Explaining why $(L, \psi)$ is not calibrated w.r.t. $0-1$ loss.}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

@@

\begin{restatable}{lemma}{polyhedralrangegamma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
  Then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
	Moreover, the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
\end{restatable}
\begin{proof}[Proof sketch]
	See \S~\ref{app:power-diagrams} for the full proof.
	As $L$ is bounded from below, $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} .
	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
	Moreover, we have $\Gamma(p)$ is exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support a face of the epigraph.
	Since this epigraph has finitely many faces as it is polyhedral, the range of $\Gamma$ is then a subset of elements of a finitely generated (finite supports) set of finite elements (finite faces).
	Moreover, each element of $\Gamma(\simplex)$ is a closed polyhedron since it corresponds exactly to a closed face of a polyhedral set.
\end{proof}

@@

\reviewer{Restated Thm 1 and gave a short proof}
\embedpolyinformal*
For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.

@@

\reviewer{Restated theorem 2 and gave formal proof}
\linkinformal*
\begin{proof}
	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
\end{proof}

@@

\reviewer{Paragraph on multiclass case, using top-$k$ with $k=1$}
Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$. 
However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
The $L^k$ surrogate simplifies to 
\begin{align*}
	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
\jessie{Does this simplify further? I don't think so}

@@

\reviewer{Forward ref}
Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by
Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\reviewer{Adding formal proof.}
\begin{proof}
	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
\end{proof}

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

\reviewer{Add commentary on $\H$ consistency and calibration}

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\raft{FYI: Added this paragraph since we needed it in \S~\ref{sec:poly-ie-consistency}}
Indirect elicitation is a weaker condition than calibration~\citep{steinwart2008support,agarwal2015consistent,finocchiaro2021unifying}; we briefly sketch the argument.
Suppose $L$ is minimizable and $(L,\psi)$ is calibrated with respect to $\ell$, and set $\Gamma=\prop{L}$ and $\gamma=\prop{\ell}$.
Let $u\in\reals^d$ and $p\in\Gamma_u$.
From eq.~\eqref{eq:calibrated}, if $\psi(u) \notin \gamma(p)$, then we would have $u\notin\Gamma(p)$, a contradiction to $p\in\Gamma_u$.
Thus, $\psi(u) \in \gamma(p)$, so $p\in\gamma_{\psi(u)}$.
In fact, indirect elicitation is strictly weaker; take hinge loss with the link $\psi(u) = -1$ for $u < 1$ and $\psi(u) = 1$ for $u\geq 1$.
\reviewerone{Comment 1}
\reviewerthree{Comment 1}
While this pair indirectly elicits the mode, we can show it is not calibrated with respect to $0-1$ loss. 
Suppose $ p  = (0, 1)$ and consider the sequence $\{1 - \frac 1 {n+1}\}_{n=1}^\infty$, which limits to $1$, but $\psi(u) = -1$ for all $u$ in the sequence.
Therefore, the infimum of hinge loss over reports not linking to $1$ approaches the infimum over all reports.
\citet{agarwal2015consistent} were the first to formally connect property elicitation to calibration, though their results generally do not apply to discrete prediction tasks.

@@

\begin{restatable}{lemma}{polyhedralrangegamma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss.
  Then $L$ is minimizable and elicits a property $\Gamma := \prop{L}$.
	Moreover, the range of $\Gamma$, given by $\Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
\end{restatable}
\begin{proof}[Proof sketch]
	See \S~\ref{app:power-diagrams} for the full proof.
	As $L$ is bounded from below, $L$ is minimizable from~\citet[Corollary 19.3.1]{rockafellar1997convex} .
	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
	Moreover, we have $\Gamma(p)$ is exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value; moreover, since the loss is polyhedral the supporting hyperplane must support a face of the epigraph.
	\reviewerone{Comment 2}
	Since this epigraph has finitely many faces as it is polyhedral, the range of $\Gamma$ is then a subset of elements of a finitely generated (finite supports) set of finite elements (finite faces).
	Moreover, each element of $\Gamma(\simplex)$ is a closed polyhedron since it corresponds exactly to a closed face of a polyhedral set.
\end{proof}

@@

\embedpolyinformal*
For a proof, observe that Theorem~\ref{thm:discrete-loss-poly-embeddable} proves the first part of the statement, and Theorem~\ref{thm:poly-embeds-discrete} shows the second.

@@

\reviewerone{Restated theorem 2 and gave formal proof}
\linkinformal*
\begin{proof}
	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
\end{proof}

@@

\reviewertwo{Comment 3}
Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$. 
However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
The $L^k$ surrogate simplifies to 
\begin{align*}
	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
\jessie{Does this simplify further? I don't think so}

@@

\reviewertwo{Forward ref}
Lemma~\ref{lem:X} now allows us to observe the relationship between embeddings, finite representative sets and polyhedral Bayes risks; we expand on this relationship in Propositions~\ref{prop:embed-bayes-risks} and \ref{prop:embed-iff-trims-equal}.
%As a finite representative set implies a polyhedral Bayes risk by Lemma~\ref{lem:loss-restrict}, Lemma~\ref{lem:X} shows that polyhedral Bayes risks are equivalent to having finite representative sets, which in turn gives an embedding by Proposition~\ref{prop:representative-embeds-restriction}.
\begin{corollary}\label{cor:poly-risk-fin-rep}
  The following are equivalent for any minimizable loss $L:\reals^d\to\reals^\Y_+$.
  \begin{enumerate}
  \item $\risk{L}$ is polyhedral.
  \item $L$ has a finite representative set.
  \item $L$ embeds a discrete loss.
  \end{enumerate}
\end{corollary}
\reviewertwo{Comment x}
\begin{proof}
	If $\risk L$ is polyhedral, then Lemma~\ref{lem:X} implies that $L$ has a finite representative set.
	Moreover, if $L$ has a finite representative set $\Sc$, then Proposition~\ref{prop:representative-embeds-restriction} implies that $L$ embeds $L|_{\Sc}$, which is finite.
	Lemma~\ref{lem:loss-restrict} additionally implies that $\risk L = \risk{L|_{\Sc}}$, which is polyhedral as the pointwise supremum of a finite set of affine functions.
\end{proof}

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.%
\reviewertwo{Comment 2}
\footnote{Polyhedral losses may be more challenging to optimize in some cases than smooth losses, so the prediction dimension may need to be much smaller, as in the BEP surrogate, until one sees a computational benefit.}
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

\paragraph{Connections to $\H$-consistency and calibration}
\reviewertwo{Comment 1}
Throughout, we establish that embedding implies calibration when restricting to the class of polyhedral losses, and use the canonical result that calibration is equivalent to consistency to establish equivalence to consistency.
However, consistency is defined by considering the optimal hypothesis over the set of all measurable functions (see \S~\ref{app:consistency}).
However, it has been established that if the hypothesis class $\H$ is restricted, a universally consistent surrogate and link pair may not be consistent over the set $\H$, or $\H$-consistent, even in the realizable setting~\citep{long2013consistency,kuznetov2014multiclass,zhang2020bayes}.
One interesting direction is to understand if (some restricted version of) ``$\H$-embeddings'' via a polyhedral surrogate implies (1) $\H$-calibration, and (2) $\H$-consistency, which are not equivalent \citep{awasthi2021calibration,awasthi2021finer}.
\citet{awasthi2022hconsistency,awasthi2022multi} study $\H$ consistency bounds for adversarial classification and multi-class classification, though it is unclear how such bounds generalize to general finite prediction tasks.

### 2023-06-09 poly-embed-journal/reviews/jmlr-response.tex
Unifying the margin comments

\raf{OLD TEXT}
  We thank the editor and reviewers for their feedback.  
  \jessie{Not sure what else to write here?}

\\
\\
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

We thank the reviewer for their thoughtful review and careful reading of our work. We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made. 
To answer the first bullet, the reviewer is correct that the pair is not calibrated; we have clarified this point in a following sentence. 
To answer their final question, each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo.

@@

\begin{itemize}
\item \textbf{Related work and discussion:}

 We thank the reviewer for the references and questions about the connections to $\H$-consistency and calibration. We have added a discussion about possible extensions to Section~\ref{sec:conclusion}. \jessie{TODO?}

\item \textbf{Questions and comments:}
  \begin{enumerate}
  \item \emph{More explanation on why a weak inequality in the definition of separated link (Definition 15) is more natural in applications such as hinge loss for binary classification.}

    Thank you; we clarified the footnote: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''

@@

    We added a footnote to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point.
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition 6, and emphasized the definition of a calibrated link in Definition 6 as well.
  We added a formal definition of consistency into the appendix with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest... let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
  We thank the reviewer for their suggestions to restate Theorems 1 and 2 where relevant; we have done so.

@@

	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}.  
	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)

>>>>

  We thank the editor and reviewers for their feedback.  
  \jessie{Not sure what else to write here?}
  \raf{TODO}

\bigskip
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

We thank the reviewer for their thoughtful review and careful reading of our work. We have incorporated the editing suggestions made, and marked in our revised manuscript where non-typo changes to the text were made. 
Below we respond to some of the clarifying questions:
\begin{enumerate}
	\item \emph{Clarify the point that indirect elicitation is strictly weaker than calibration}

	See margin comment 1 in orange.

	\item \emph{Proof of Lemma~\ref{lem:polyhedral-range-gamma}}

	The reviewer is correct on all the suggestions; we have made changes accordingly.
	See margin comment 2 in orange for how we rephrased the sentence with too many parentheticals.

	\item \emph{``Thus, for any $u \in \cup \mathcal{U}$''}

	Each element of $\mathcal{U}$ is a set, so the union $\cup \mathcal{U}$ is a set of real-valued $v \in \mathbb{R}^d$; hence it is not a typo. 
\end{enumerate}

@@

\begin{itemize}
\item \textbf{Related work and discussion:}\\
 We thank the reviewer for the references and questions about the connections to $\mathcal{H}$-consistency and calibration. We have added a discussion about possible extensions to Section~\ref{sec:conclusion}. See margin comment 1 in blue.

\item \textbf{Questions and comments:}
  \begin{enumerate}
  \item \emph{More explanation on why a weak inequality in the definition of separated link (Definition~\ref{def:sep-link}) is more natural in applications such as hinge loss for binary classification.}

    Thank you; we clarified footnote 2: ``For example, taking hinge loss for binary classification, the sign link is 1-separated under the weak inequality, but only $(1-\delta)$-separated for $\delta > 0$ under the strict inequality.''

@@

    We added footnote 7 to the ``Polyhedral vs.\ smooth'' paragraph in the discussion to make the reviewer's excellent point. 
    (See margin comment 2 in blue.)
    In general, we lack frameworks which can combine optimization tradeoffs with statistical tradeoffs, making it hard to say whether and when smooth vs polyhedral losses will lead to better computational or statistical performance.
    These questions appear challenging and heavily dependent on the setting (e.g.\ how costly data acquisition vs computation is).

@@

    We are not sure what the reviewer means by ``a Weston--Watkins polyhedral loss'', since we had thought of the Weston--Watkins hinge as a specific surrogate.
    But taking the question to mean ``is there a polyhedral surrogate consistent for 0--1 loss in multiclass settings?'', we added a brief discussion at the end of Section 5.5 (``Surrogates for top-k classification'') giving such a hinge-like surrogate, a special case of the top-$k$ version with $k=1$.
    See margin comment 3.

@@

  We have fixed all minor issues.
  We added the definition of a link function to Definition~\ref{def:calibrated}, and emphasized the definition of a calibrated link in Definition~\ref{def:calibrated} as well.
  We added a formal definition of consistency into Appendix~\ref{app:consistency} with discussion about this definition and its history.\raft{I'm actually wondering if we should just define it in the paper like they suggest... let's see how the appendix section turns out} \jessiet{based on first pass of appendix section, might be in favor of adding in to body.}
  We thank the reviewer for their suggestions to restate Theorems~\ref{thm:embed-poly-main} and \ref{thm:link-main} where relevant; we have done so.

@@

	The choice of surrogate loss is of course important for consistency, but so is the choice of link function; see the discussion after Definition~\ref{def:indirect-elic}, marked by margin comment 1 in green.  
	(In particular, it seems the reviewer may be fixing the link to be the sign function; e.g. logistic loss is consistent with respect to 0-1 loss when using the sign link, but not with any other link.)
